Figure 2. Bacterial Communities and Function

### 2022-01-06 reports/rmarkdown/manuscript/Figure2.Rmd
Correcting spelling

barlist( data = rbind(WS=mL ,
                      "16S counts"=xL),
         genes = c("WS","16S counts"),
         clustering = group_annotation,srt=20,
         draw_mean_lines=F,col = pal)
mtext("Lactobacillus", side=3, las = 1, cex = .6, line = .5,xpd=T)
mtext("Wett Smear Bacteria Validation", side=3, las = 1, cex = .6, line =1.5,xpd=T, font = 2)

>>>>

barlist( data = rbind(WS=mL ,
                      "16S counts"=xL),
         genes = c("WS","16S counts"),
         clustering = group_annotation,srt=20,
         draw_mean_lines=F,col = pal)
mtext("Lactobacillus", side=3, las = 1, cex = .6, line = .5,xpd=T)
mtext("Wet Smear Bacteria Validation", side=3, las = 1, cex = .6, line =1.5,xpd=T, font = 2)
